---
title: "LogisticRegressionPractical"
output: html_document
---

# Pre-amble

## Library

```{r Library}
library(haven)
library(psych)
library(knitr)
library(broom)
```

## Import dataset

Import dataset

```{r Import Dataset}
DiabetesDS <- read_dta("diabetes.dta")
kable(head(DiabetesDS))
```

There is three variables with categorical data, but recorded as numerical.  

Need to convert categorical data

```{r Convert Categorical Data}
DiabetesDS$dmdx2 <- as_factor(DiabetesDS$dmdx)
DiabetesDS$gender2 <- as_factor(DiabetesDS$gender)
DiabetesDS$crural2 <- as_factor(DiabetesDS$crural)
```

View updated dataset

```{r View Dataset}
kable(summary(DiabetesDS [, 20:22]))
kable(describe(DiabetesDS))
```

# Logistic Regression Modelling

## Simple Logistic Regression

### Model01 - age

Model01

- Outcome: Diabetes Status (dmdx2)
- predictor: age (numerical)

```{r SLogR age}
Model01 <- glm(dmdx2 ~ age, family = binomial(link = 'logit'),
               data = DiabetesDS)
summary(Model01)
kable(tidy(Model01))
```

### Model02 - gender

Model02

- outcome: DM status
- predictor: gender

```{r SLogR gender}
Model02 <- glm(dmdx2 ~ gender2, family = binomial(link = "logit"),
               data = DiabetesDS)
summary(Model02)
kable(tidy(Model02))
```

## Multiple Logistic Regression

### Model11 - age & gender

Model11

- outcome: DM Status
- predictor: age (numerical) & gender (categorical)

```{r MLogR Age & Gender}
Model11 <- glm(dmdx2 ~ age + gender2, family = binomial(link = "logit"),
               data = DiabetesDS)
summary(Model11)
kable(tidy(Model11))
```

### Model12 - age, gender & interaction

Model12

- outcome: DM Status
- predictor: age, gender, age*gender interaction term

```{r MLogR Age Gender & Age*Gender}
Model12 <- glm(dmdx2 ~ age + gender2 + age:gender2, family = binomial(link = "logit"),
               data = DiabetesDS)
summary(Model12)
kable(tidy(Model12))
```

## Confidence Interval

find CI for Model11

- outcome: DM Status
- predictor: age (numerical) & gender (categorical)

```{r CI Model11}
kable(confint(Model11))
```

## Odd Ratio

Calculate OR and 95% CI for OR

```{r OR & CI OR}
Table_Model11 <- tidy(Model11)
OR_Model11 <- exp(coefficients(Model11))
ORCI_Model11 <- exp(confint(Model11))
kable(cbind(Table_Model11, OR_Model11, ORCI_Model11))
```

