---
title: "LoGRTryLong"
author: "Mohd Azmi"
date: "01/11/2019"
output: 
  html_document:
    toc: yes
    toc_float:
      collapsed: no
---

# Pre-amble

## Library

```{r Library, message=F}
library(haven)
library(knitr)
library(tidyr)
library(psych)
library(ggplot2)
library(dplyr)
library(broom)
library(corrplot)
library(mfp)
library(generalhoslem)
library(ResourceSelection)
library(LogisticDx)
```

## Dataset

Import dataset

```{r Import Dataset}
LogDS <- read_dta("diabetes.dta")
kable(head(LogDS))
```

Convert categorical data

```{r Convert Categorical Data}
LogDS$dmdxcat <- as_factor(LogDS$dmdx)
LogDS$gendercat <- as_factor(LogDS$gender)
LogDS$cruralcat <- as_factor(LogDS$crural)
kable(head(LogDS))
```

alternatively, dplyr::mutate can also be use

```{r convert alternative}
LogDS2 <- LogDS %>%
  mutate (dmdxcat = as_factor(dmdx),
          gendercat = as_factor(gender),
          cruralcat = as_factor(crural))
kable(head(LogDS2))
```



# Data Exploration

## Data summary

```{r Data Summary, message=F}
kable(summary(LogDS [, 20:22]))
summary(LogDS)
kable(describe(LogDS [, c(2, 4:10, 12)]))
```
## Data Visualization

Histogram for numerical data

```{r Historgram numerical, message=F}
ggplot(LogDS, aes(age)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$age),
                            sd = sd(LogDS$age)))
ggplot(LogDS, aes(height)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$height),
                            sd = sd(LogDS$height)))

ggplot(LogDS, aes(weight)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$weight),
                            sd = sd(LogDS$weight)))

ggplot(LogDS, aes(hba1c)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$hba1c),
                            sd = sd(LogDS$hba1c)))

ggplot(LogDS, aes(fbs)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$fbs),
                            sd = sd(LogDS$fbs)))

ggplot(LogDS, aes(mogtt2h)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$mogtt2h),
                            sd = sd(LogDS$mogtt2h)))

ggplot(LogDS, aes(totchol)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$totchol),
                            sd = sd(LogDS$totchol)))

ggplot(LogDS, aes(ftrigliz)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$ftrigliz),
                            sd = sd(LogDS$ftrigliz)))

ggplot(LogDS, aes(hdl)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$hdl),
                            sd = sd(LogDS$hdl)))

ggplot(LogDS, aes(ldl)) +
  geom_histogram(aes(y=..density..)) +
  stat_function(fun = dnorm, colour = "red",
                args = list(mean = mean(LogDS$ldl),
                            sd = sd(LogDS$ldl)))
```

Bar chart for categorical data

```{r Barchart categorical}
ggplot(LogDS, aes(dmdxcat)) +
  geom_bar()
ggplot(LogDS, aes(gendercat)) +
  geom_bar()
ggplot(LogDS, aes(cruralcat)) +
  geom_bar()
```

Correlation Matrix among Numerical Data

```{r Corrplot for Numerical Data}
LogDS_Num <- LogDS %>%
  select_if(is.numeric)
Cor_LogDS_Num <- cor(LogDS_Num, use = "complete.obs", method = "pearson")
kable(round(Cor_LogDS_Num,2))
corrplot(Cor_LogDS_Num)
```



# Logistic Regression Modelling

## Univariable - Simple Logistic Regression

### Model01 - age

Model01

- outcome: dmstatus
- predictor - age

```{r SLogR Age}
Model01 <- glm(dmdxcat ~ age,
               data = LogDS,
               family = binomial (link = "logit"))
summary(Model01)
kable(tidy(Model01))
names(Model01)
```

### Model02 - Gender

Model02

- outcome: dm status
- predictor - gender

```{r SLogR Gender}
Model02 <- glm(dmdxcat ~ gender,
               data = LogDS,
               family = binomial (link = "logit"))
summary(Model02)
kable(tidy(Model02))
```

## Multivariable - Multiple Logistic Regression

### Model11 - age & gender

Model11

- outcome: dm
- predictor: age, gender

```{r MLogR Age Gender}
Model11 <- glm(dmdxcat ~ age + gendercat,
               family = binomial(link = "logit"),
               data = LogDS)
summary(Model11)
kable(tidy(Model11))
```

Calculate OR and 95% CI

```{r OR for Model11, message=F}
Table_Model11 <- tidy(Model11)
OR_Model11 <- exp(coefficients(Model11))
ORCI_Model11 <- exp(confint(Model11))
kable(cbind(Table_Model11 [, 1:5], OR_Model11, ORCI_Model11))
```

## Inference - MLE method (Wald Test)

### Wald Test for Age

$W = \beta/SE_\beta$

Example 1, calculate Wald test for Model01 (age)

```{r Wald for SLogR Age}
0.0511159/0.0038629
```

p-value for above.

```{r p-value for W test Model01}
2*pnorm(-abs(0.0511159/0.0038629))
```


### Wald Test for Gender

Wald Test for Model02 (gender)

```{r Wald for SLogR Gender}
0.2222904/0.1025100
```

p-value for above

```{r p-value for W test Model02}
2*pnorm(-abs(0.2222904/0.1025100))
```

## Inference - SE method (Confident Interval)

### CI for Age

CI for Model01

```{r CI for Model01}
kable(tidy(confint(Model01)))
```

the confident interval didn't cross 1

## Inference - Likelihood Ratio Test

### LR Test fot Model01 with Model11

- Model01 - age as covariate
- Model11 - age and gender as covariate

to explore LR when gender is added to Model01

```{r LR test CoV gender}
anova(Model11, Model01, test="Chisq")
```

### LR Test fot Model02 with Model11

- Model02 - gender as covariate
- Model11 - age and gender as covariate

to explore LR when age is added to Mofrl02

```{r LR test CoV age}
anova(Model11, Model02, test="Chisq")
```

## Model Selection

### Explore Univariable

```{r}
SLogMod_AgeBPSugar <- LogDS %>%
  dplyr::select(age, msbpr, mdbpr, fbs, mogtt2h, hdl) %>%
  purrr::map(~glm(dmdxcat ~ .x,
                  family = binomial,
                  data = LogDS)) %>%
  purrr::map(tidy) %>%
  bind_rows()
ResultSLogMod01 <- SLogMod_AgeBPSugar %>%
  mutate(model = c("b0", "age",
                   "b0", "msbpr",
                   "b0", "mdbpr",
                   "b0", "fbs",
                   "b0", "mogtt2h",
                   "b0", "hdl")) %>%
  dplyr::select(model, everything())
kable(ResultSLogMod01)
```

### Explore Multicollinearity & Confounder

Correlation Matrix

Correlation Matrix among msbp, dbp, fbs & mogtt2h

```{r Corrplot for BP and Sugar}
LogDS_BPSugar <- LogDS %>%
  dplyr::select("msbpr", "mdbpr", "fbs", "mogtt2h")
Cor_LogDS_BPSugar <- cor(LogDS_BPSugar, use = "complete.obs", method = "pearson")
kable(round(Cor_LogDS_BPSugar,2))
corrplot(Cor_LogDS_BPSugar)
pairs(LogDS_BPSugar)
```

### Model21 - age, msbp, fbs, hdl

```{r Model21}
Model21 <- glm(dmdxcat ~ age + msbpr + fbs + hdl,
               family = binomial(link = "logit"),
               data = LogDS)
summary(Model21)
kable(tidy(Model21))
```

sbp not significant

### Model22 - age, dbp, fbs, hdl

```{r Model22}
Model22 <- glm(dmdxcat ~ age + mdbpr + fbs + hdl,
               family = binomial(link = "logit"),
               data = LogDS)
summary(Model22)
kable(tidy(Model22))
```

dbp significant

### Model32 - age, dbp, fbs, hdl, mogtt

```{r Model32}
Model32 <- glm(dmdxcat ~ age + mdbpr + fbs + hdl + mogtt2h,
               family = binomial(link = "logit"),
               data = LogDS)
summary(Model32)
kable(tidy(Model32))
```

mogtt as confounder?

#### Confounder fbs

Model22 - age, dbp, fbs, hdl

```{r Confounder fbs}
Model22_01 <- tidy(Model22)
Model32_01 <- tidy(Model32)
((Model32_01[2,2] - Model22_01[2,2])/Model22_01[2,2])*100
```

#### Confounder mogtt

Model23 - age, dbp, mogtt, hdl

```{r Model23}
Model23 <- glm(dmdxcat ~ age + mdbpr + mogtt2h + hdl,
               family = binomial(link = "logit"),
               data = LogDS)
Model23_01 <- tidy(Model23)
((Model32_01[2,2]-Model23_01[2,2])/Model23_01[2,2])*100
```

mogtt has higher changes, thus mogtt selected as compared to fbs

### Model23 - age, dbp, mogtt, hdl

```{r rerun Model23}
summary(Model23)
kable(tidy(Model23))
```

### Explore Interaction

Preliminary Main Effect Model - Model41

- outcome: dm
- covariate: age, dbp, fbs, gender

Simple Logistic Regression for each covariates

```{r SLogR Mode41}
SLogR_Model41 <- LogDS %>%
  dplyr::select(age, mdbpr, fbs, gendercat) %>%
  purrr::map(~glm(dmdxcat ~ .x,
                  family = binomial,
                  data = LogDS)) %>%
  purrr::map(tidy) %>%  bind_rows()

ResultSLogRMod41 <- SLogR_Model41 %>%
  mutate(model = c("b0", "age",
                   "b0", "mdbpr",
                   "b0", "fbs",
                   "b0", "gendercat")) %>%
  dplyr::select(model, everything())
kable(ResultSLogRMod41)
```

Multiple Logistic Regression

```{r MLogR Model41}
Model41 <- glm(dmdxcat ~ age + mdbpr + fbs + gendercat,
               family = binomial(link = "logit"),
               data = LogDS)
summary(Model41)
kable(tidy(Model41))
```


#### Interaction 1 - age:dbp

Interaction 1 - age:dbp

- covariate: age, dbp, fbs, gender, age:dbp

```{r Interaction age:dbp}
Model41_Int01 <- glm(dmdxcat ~ age + mdbpr + fbs + gendercat + age:mdbpr,
                     family = binomial(link = "logit"),
                     data = LogDS)
summary(Model41_Int01)
kable(tidy(Model41_Int01))
```

interaction term not significant

#### Interaction 2 - age:fbs

- covariate: age, dbp, fbs, gender, age:fbs

```{r Interaction age:fbs}
Model41_Int02 <- glm(dmdxcat ~ age + mdbpr + fbs + gendercat + age:fbs,
                     family = binomial(link = "logit"),
                     data = LogDS)
summary(Model41_Int02)
kable(tidy(Model41_Int02))
```

interaction term not significant

#### Interaction 3 - age:gender

- covariate: age, dbp, fbs, gender, age:gender

```{r Interaction age:gender}
Model41_Int03 <- glm(dmdxcat ~ age + mdbpr + fbs + gendercat + age:gendercat,
                     family = binomial(link = "logit"),
                     data = LogDS)
summary(Model41_Int03)
kable(tidy(Model41_Int03))
```

interaction term not significant

#### Interaction 4 - dbp:fbs

- covariate: age, dbp, fbs, gender, dbp:fbs

```{r Interaction dbp:fbs}
Model41_Int04 <- glm(dmdxcat ~ age + mdbpr + fbs + gendercat + mdbpr:fbs,
                     family = binomial(link = "logit"),
                     data = LogDS)
summary(Model41_Int04)
kable(tidy(Model41_Int04))
```

interaction term is significant

#### Interaction 5 - dbp:gender

- covariate: age, dbp, fbs, gender, dbp:gender

```{r Interaction dbp:gender}
Model41_Int05 <- glm(dmdxcat ~ age + mdbpr + fbs + gendercat + mdbpr:gendercat,
                     family = binomial(link = "logit"),
                     data = LogDS)
summary(Model41_Int05)
kable(tidy(Model41_Int05))
```

interaction is not significant

#### Interaction 6 - fbs:gender

- covariate: age, dbp, fbs, gender, fbs:gender

```{r Interaction fbs:gender}
Model41_Int06 <- glm(dmdxcat ~ age + mdbpr + fbs + gendercat + fbs:gendercat,
                     family = binomial(link = "logit"),
                     data = LogDS)
summary(Model41_Int06)
kable(tidy(Model41_Int06))
```

no interaction

### Prelim Final Model

Preliminary Final Model

- outcome: dm
- predictor: age, dbp, fbs, gender, dbp:cholesterol

```{r}
PrelimFinalModel <- glm(dmdxcat ~ age + mdbpr + totchol + gendercat + mdbpr:totchol,
                        family = binomial(link = "logit"),
                        data = LogDS)
summary(PrelimFinalModel)
kable(tidy(PrelimFinalModel))
```

Model matrix for PrelimFinalModel

```{r model matrix PrelimFinalModel}
kable(head(model.matrix(PrelimFinalModel)))
```


#### Predicted value - raw predicted (logit)

Raw Predicted Values (logit) = a+bx

```{r}
logitPredProb_PrelimModel <- predict(PrelimFinalModel, type="link")
kable(head(logitPredProb_PrelimModel))
```

#### Predicted value - odds predicted ()

odds predicted = exp(a+bx) 

```{r}
PredProb_PrelimModel <- fitted(PrelimFinalModel)
kable(head(PredProb_PrelimModel))
```

alternatively
```{r}
PredProbAlt_PrelimModel <- predict(PrelimFinalModel, type = "response")
kable(head(PredProbAlt_PrelimModel))
```


#### Residual - raw

raw residual

```{r raw residual}
kable(head(augment(PrelimFinalModel)))
```

probability residual

```{r Prob Residual PrelimFinalModel}
kable(head(augment(PrelimFinalModel,
                   type.predict="response",
                   type.residual="respone")))
```


## Model Checking

### Hosmer Lemeshow Test


```{r HL test for Prelim Final Model}
logitgof(LogDS$dmdx, fitted(PrelimFinalModel), g = 10)
hoslem.test(LogDS$dmdxcat, fitted(PrelimFinalModel), g = 10)
HLT_PrelimModel <- dx(PrelimFinalModel, byCov = T)
kable(tail(HLT_PrelimModel))
```

### Diagnostic Plot

```{r}
PrelimFinalModel
plot(PrelimFinalModel)
```

### ROC Curve

```{r}
gof_PrelimModel <- gof(PrelimFinalModel, plotROC = T)
gof_PrelimModel
gof_PrelimModel$auc
```

#### Chisquare for Goodness of fitness 

```{r}
kable(gof_PrelimModel$chiSq)
```

HL not significant - model is fit

#### Hosmer Lemeshow Test Contingency Table

```{r}
kable(gof_PrelimModel$ctHL)
```

summary of GOF tests

```{r}
kable(gof_PrelimModel$gof)
```


## Linearity in Logit



